\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-01 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
graphs E2-E4
Signed-off-by: Guillaume Daudin <gdaudin@mac.com>

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects), Manufacturing}
\label{fig:totalTC_compeffects_excl_manuf}
\begin{center}
\includegraphics[height=8cm] {graph_composition_manuf.pdf}
\end{center}
\end{figure}

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects), Primary goods}
\label{fig:totalTC_compeffects_excl_primary}
\begin{center}
\includegraphics[height=8cm]
{graph_composition_primary.pdf}
\end{center}
\end{figure}

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects)}
\label{fig:totalTC_compeffects_excl}
\begin{center}
\includegraphics[height=8cm]
{graph_composition_all.pdf}
\end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects), Manufacturing}
\label{fig:totalTC_compeffects_excl_manuf}
\begin{center}
\includegraphics[height=8cm] {../graph_composition_manuf.jpg}
\end{center}
\end{figure}

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects), Primary goods}
\label{fig:totalTC_compeffects_excl_primary}
\begin{center}
\includegraphics[height=8cm]
{../graph_composition_primary.jpg}
\end{center}
\end{figure}

\begin{figure}[htbp]
\caption{Transport costs (with and without composition effects)}
\label{fig:totalTC_compeffects_excl}
\begin{center}
\includegraphics[height=8cm]
{../graph_composition_all.jpg}
\end{center}
\end{figure}
